Multi-Robot Probabilistic Mapping and Exploration

### 2018-06-26 Dissertation/Thesis/tex/frontmatter.tex
added mapping background & beginning of autonomous exploration lit review
fixed committee members in frontmatter

@@

Yin-Lin Shen\\
Department of Mechanical and Aerospace Engineering\\
The George Washington University\\ 
Committee Member
}

@@

Finally, I would like to thank my research advisor, Taeyoung Lee, for the excellent guidance over the last six years. Unlike many relationships between advisors and students, we treats his students like colleagues rather than subordinates. This way, I could focus on completing my research objectives properly rather than trying to impress superior figure. Taeyoung Lee knew just what to say to push my research forward, even when my mind was going another direction. His positive influence over my research has been unparalleled, and I will continue using his valuable lessons.% in the years to come.

>>>>

Robert Pless\\
Department of Computer Science\\
The George Washington University\\
Committee Member\\

@@

Chung Hyuk Park\\
Department of Biomedical Engineering\\
The George Washington University\\ 
Committee Member\\

Zhuming Ai\\
Information Management and Decision Architectures\\
U.S. Naval Research Laboratory\\ 
Committee Member

@@

Finally, I would like to thank my research advisor, Taeyoung Lee, for the excellent guidance over the last six years. Unlike many relationships between advisors and students, he has treated his students like colleagues rather than subordinates. This way, I could focus on completing my research objectives properly rather than trying to impress superior figure. Taeyoung Lee knew just what to say to push my research forward, even when my mind was going another direction. His positive influence over my research has been unparalleled, and I will continue using his valuable lessons.% in the years to come.
